Model Recognition as Planning

### 2019-03-10 doc/icaps-19/camera-ready/model-recognition.tex
ICAPS19:minor changes

As an example, imagine you are given a set of models, each one encoding a different navigation policy for a $N\times N$ grid. Figure~\ref{fig:model-example} shows an example of one such model, according to which, the agent can only move right when he is at an even row ({\tt\small $q0$} holds), and left when he is at an odd row ({\tt\small $q1$} holds). Given the partially observed plan execution of Figure~\ref{fig:grid-example}, where variables {\small\tt $q0$} and {\small\tt $q1$} are unobserved, model recognition aims to identify the navigation policy (model) that better explains this observation.

@@

\subsection*{Acknowledgement}
This work is supported by the Spanish MINECO project TIN2017-88476-C2-1-R. Diego Aineto is partially supported by the {\it FPU16/03184} and Sergio Jim\'enez by the {\it RYC15/18009}, both programs funded by the Spanish government. M. Ramirez research is partially funded by DST Group Joint \& Operations Analysis Division.

>>>>

As an example, imagine you are given a set of models, each one encoding a different navigation policy for a $N\times N$ grid. Figure~\ref{fig:model-example} shows an example of one such model, according to which, the agent can only move right when it is at an even row ({\tt\small $q0$} holds), and left when it is at an odd row ({\tt\small $q1$} holds). Given the partially observed plan execution of Figure~\ref{fig:grid-example}, where variables {\small\tt $q0$} and {\small\tt $q1$} are unobserved, model recognition aims to identify the navigation policy (model) that better explains this observation.

@@

\subsection*{Acknowledgements}
This work is supported by the Spanish MINECO project TIN2017-88476-C2-1-R. Diego Aineto is partially supported by the {\it FPU16/03184} and Sergio Jim\'enez by the {\it RYC15/18009}, both programs funded by the Spanish government. M. Ramirez research is partially funded by DST Group Joint \& Operations Analysis Division.
